---
title: "Final Project"
author: "Keeley MacAfee"
date: "10/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(janitor)
```

```{r}
expenditures <- read_excel("./data/nominal_expenditures.xlsx", skip = 4) %>%
  clean_names() %>%
  head(21)

expenditures_no_taxes_tips <- read_excel("./data/nominal_expenditures_no_taxes_tips.xlsx", skip = 4) %>%
  clean_names() %>%
  head(21)

expenditures_alcohol <- expenditures %>%
     select(year, drinking_places, hotels_and_motels, liquor_stores, eating_and_drinking_places)
   
expenditures_nt_alcohol <- expenditures_no_taxes_tips %>%
    select(year, drinking_places, hotels_and_motels, liquor_stores, eating_and_drinking_places)

expenditures_nt_alcohol %>%
  ggplot(aes(x = year, y = hotels_and_motels)) + geom_point() + geom_smooth()

```
 
This data set is from the USDA's current food expenditures series. I plan to run analysis on certain variables, like expenditure at grocery stores, gas stations, etc., to assess the changes in spending on food and alcohol in different capacities. I have worked with consumer trends in the context of professional athletics, and I am interested in using this data to draw conclusions about more day-to-day consumer behaviors.

